manuscript - APP

### 2018-10-03 R/manuscript_app.Rmd
update analysis regarding exp 2

```{r exp 2a - overall differences, warning=F, message = F}
df_exp2a %>% 
  filter(restk2 == "Slow-moving-distractors") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = type, 
        detailed = T) %>% 
  apa::anova_apa()

>>>>

```{r exp 2a - overall differences, warning=F, message = F}
df_exp2a %>% 
  filter(restk2 == "Slow-moving-distractors") %>% 
  ez::ezANOVA(dv = accuracy,
        wid = subject,
        within = as.type, 
        detailed = T) %>% 
  apa::anova_apa()
